R Notebook

### 2021-07-26 Paper_Figure_code.Rmd
Updates
Removes legend background on Figure 3
Figures are properly labelled in the code
Add titles for better navigation
Other things probably

---
title: "R Notebook"
output: html_notebook
---

@@

################ Start Figure 2 and Figure S1-S2################

@@

load("~/deconvolution/Final methylation paper/figure/Figure2 and S1_S2/Figure2_RawData.RData")

out.l <- epidish(GSE132203_100, BPmet, "RPC", maxit = 100)
GSE132203_100_BPmet <- data.frame(out.l$estF[,c(2,3,4,1,6,5)])

@@

melt_GSE132203_100_BPmet <- melt(GSE132203_100_BPmet) %>% cbind(melt_FACS_GSE132203_100$value, .)
colnames(melt_GSE132203_100_BPmet) <- c("FACS","cell_type","ALL")

p_GSE132203_100_BPmet_all <- ggplot(melt_GSE132203_100_BPmet,aes(x=FACS, y=ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(2,3,4,1,6,5)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)

p_GSE132203_100_BPmet_all_longly <- ggplot(melt_GSE132203_100_BPmet,aes(x=FACS, y=ALL, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "BPmet") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.95), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(2,3,4,1,6,5)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)

@@

colnames(GSE132203_100_BPmet)<-c("V","V","V","V","V","V","CD4","CD8","Mono","B","NK","Neu")

@@

for (i in c(1:6)) {

    rmse[[i]] <- rmse(GSE132203_100_BPmet[,i], FACS_GSE132203_100[,i])

    melt_GSE132203_100_BPmet[[i]] <- melt(GSE132203_100_BPmet[,c(i, i+6)],  id.vars = colnames(GSE132203_100_BPmet)[i], measure.vars = colnames(GSE132203_100_BPmet)[i+6])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
                   rmse = unlist(rmse))

p_GSE132203_100_BPmet[[1]] <-  ggplot(melt_GSE132203_100_BPmet[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL ) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.33, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.078, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[2]] <- ggplot(melt_GSE132203_100_BPmet[[2]],aes(x=value, y= V)) + geom_point(colour = c("green"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.5)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.5, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.42, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.075, y = 0.34, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2],2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[3]] <-  ggplot(melt_GSE132203_100_BPmet[[3]],aes(x=value, y= V)) + geom_point(colour = c("blue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.3)) + scale_y_continuous(name = NULL, limits = c(0,0.4)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.4, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.33, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.074, y = 0.26, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3],2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[4]] <- ggplot(melt_GSE132203_100_BPmet[[4]],aes(x=value, y= V)) + geom_point(colour = c("darkgoldenrod1"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.2)) + scale_y_continuous(name = NULL, limits = c(0,0.3)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.248, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.050, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4],2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[5]] <- ggplot(melt_GSE132203_100_BPmet[[5]],aes(x=value, y= V)) + geom_point(colour = c("darkmagenta"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,0.15)) + scale_y_continuous(name = NULL, limits = c(0,0.2)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.2, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.165, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", 0.039, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5],2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[6]] <-ggplot(melt_GSE132203_100_BPmet[[6]],aes(x=value, y= V)) + geom_point(colour = c("deepskyblue"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 1, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.82, size = 6)  +  theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5)) + annotate("text", x = 0.26, y = 0.68, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6],2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet_each <- ggarrange(p_GSE132203_100_BPmet[[1]],p_GSE132203_100_BPmet[[2]],p_GSE132203_100_BPmet[[3]],p_GSE132203_100_BPmet[[4]],p_GSE132203_100_BPmet[[5]],p_GSE132203_100_BPmet[[6]], ncol = 2, nrow=3)

figure_GSE132203_100_BPmet_each_together <- ggarrange(p_GSE132203_100_BPmet_all, p_GSE132203_100_BPmet_each, ncol = 2, nrow=1, labels = "a", font.label = list(size = 20, color = "black"), widths = c(1,2))

figure_GSE132203_100_BPmet_each_together <- annotate_figure(figure_GSE132203_100_BPmet_each_together, left = text_grob("BPmet estimate", color = "black", size = 20, rot = 90))

```

@@

GSE132203_100_MethylCIBERSORT_WB <- as.data.frame(cbind(out.l$estF[,3] + out.l$estF[,10], out.l$estF[,5], out.l$estF[,1], out.l$estF[,2], out.l$estF[,4], out.l$estF[,9]))

@@

melt_GSE132203_100_MethylCIBERSORT_WB <- melt(GSE132203_100_MethylCIBERSORT_WB) %>% cbind(melt_FACS_GSE132203_100$value, .)
colnames(melt_GSE132203_100_MethylCIBERSORT_WB) <- c("FACS","cell_type","MethylCIBERSORT")

p_GSE132203_100_MethylCIBERSORT_WB_all <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB,aes(x=FACS, y=MethylCIBERSORT, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "ALL") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, limits = c(0,1)) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(3,5,1,2,4,9)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)

p_GSE132203_100_MethylCIBERSORT_WB_all_lonly <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB,aes(x=FACS, y=MethylCIBERSORT, colour = cell_type)) + geom_point(shape = 19 ,size=4) + theme_bw() + scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) + stat_smooth(method = lm,color="black") + facet_wrap(~ "MethylCIBERSORT") + scale_x_continuous(name = NULL, limits = c(0,1)) + scale_y_continuous(name = NULL, labels =NULL, breaks = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black")  + theme(axis.title.x = element_text(vjust=-0.5)) + theme(axis.title.y = element_text(vjust=1.5))  + theme(legend.justification=c(0.05,0.95), legend.position=c(0.05,0.96), legend.title=element_blank(), legend.key.size = unit(0.8, "cm"))  + annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[,c(3,5,1,2,4,9)], FACS_GSE132203_100)$est,3)), parse = F, size = 8)
#### each cell types

@@

colnames(GSE132203_100_MethylCIBERSORT_WB)<-c("V","V","V","V","V","V","CD4","CD8","Mono","B","NK", "Neu")

@@

for (i in c(1:6)) {

    rmse[[i]] <- rmse(GSE132203_100_MethylCIBERSORT_WB[,i], GSE132203_100_MethylCIBERSORT_WB[,i+6])

    melt_GSE132203_100_MethylCIBERSORT_WB[[i]] <- melt(GSE132203_100_MethylCIBERSORT_WB[,c(i, i+6)],  id.vars = colnames(GSE132203_100_MethylCIBERSORT_WB)[i], measure.vars = colnames(GSE132203_100_MethylCIBERSORT_WB)[i+6])
}

RMSE <- data.frame(cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
                   rmse = unlist(rmse))

p_GSE132203_100_MethylCIBERSORT[[1]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[1]],aes(x=value, y= V)) + geom_point(colour = c("red"), size = 6) + theme_bw() + stat_smooth(method = lm,color="black") + facet_wrap(~ variable)+ scale_x_continuous(name = NULL) + scale_y_continuous(name = NULL) + theme(strip.text.x = element_text(size=18, color = "black", face="bold"),  text = element_text(size = 20)) + font("xy.text", size = 16, color = "black") + stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = '\n')), label.x = 0, label.y = 0.3, size = 6) + stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = '\n')), label.x = 0, label.y = 0.245, size = 6)  + theme(axis.title.y = element_text(vjust=1.5)) +  theme(axis.title.x = element_text(vjust=-0.5)) + annotate("text", x = 0.078, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1],2))))), parse = TRUE, size = 6)

>>>>

---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

@@

# Start Figure 3 and Figure S1-S2

@@

load("~/Documents/Ting_paper/Code/all_figures/Figure2 and S1_S2/Figure2_RawData.RData")

out.l <- epidish(GSE132203_100, BPmet, "RPC", maxit = 100)
GSE132203_100_BPmet <- data.frame(out.l$estF[, c(2, 3, 4, 1, 6, 5)])

@@

melt_GSE132203_100_BPmet <- melt(GSE132203_100_BPmet) %>% cbind(melt_FACS_GSE132203_100$value, .)
colnames(melt_GSE132203_100_BPmet) <- c("FACS", "cell_type", "ALL")

p_GSE132203_100_BPmet_all <- ggplot(melt_GSE132203_100_BPmet, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~"ALL") +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, limits = c(0, 1)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(2, 3, 4, 1, 6, 5)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)

p_GSE132203_100_BPmet_all_longly <- ggplot(melt_GSE132203_100_BPmet, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~"BPmet") +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, limits = c(0, 1)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(2, 3, 4, 1, 6, 5)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)

@@

colnames(GSE132203_100_BPmet) <- c("V", "V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK", "Neu")

@@

for (i in c(1:6)) {
  rmse[[i]] <- rmse(GSE132203_100_BPmet[, i], FACS_GSE132203_100[, i])

  melt_GSE132203_100_BPmet[[i]] <- melt(GSE132203_100_BPmet[, c(i, i + 6)], id.vars = colnames(GSE132203_100_BPmet)[i], measure.vars = colnames(GSE132203_100_BPmet)[i + 6])
}

RMSE <- data.frame(
  cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
  rmse = unlist(rmse)
)

p_GSE132203_100_BPmet[[1]] <- ggplot(melt_GSE132203_100_BPmet[[1]], aes(x = value, y = V)) +
  geom_point(colour = c("red"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.33, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.078, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[2]] <- ggplot(melt_GSE132203_100_BPmet[[2]], aes(x = value, y = V)) +
  geom_point(colour = c("green"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.5, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.42, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.075, y = 0.34, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[3]] <- ggplot(melt_GSE132203_100_BPmet[[3]], aes(x = value, y = V)) +
  geom_point(colour = c("blue"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.33, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.074, y = 0.26, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[4]] <- ggplot(melt_GSE132203_100_BPmet[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.248, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.050, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[5]] <- ggplot(melt_GSE132203_100_BPmet[[5]], aes(x = value, y = V)) +
  geom_point(colour = c("darkmagenta"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.165, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", 0.039, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[6]] <- ggplot(melt_GSE132203_100_BPmet[[6]], aes(x = value, y = V)) +
  geom_point(colour = c("deepskyblue"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, limits = c(0, 1)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.82, size = 6) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  annotate("text", x = 0.26, y = 0.68, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet_each <- ggarrange(p_GSE132203_100_BPmet[[1]], p_GSE132203_100_BPmet[[2]], p_GSE132203_100_BPmet[[3]], p_GSE132203_100_BPmet[[4]], p_GSE132203_100_BPmet[[5]], p_GSE132203_100_BPmet[[6]], ncol = 2, nrow = 3)

figure_GSE132203_100_BPmet_each_together <- ggarrange(p_GSE132203_100_BPmet_all, p_GSE132203_100_BPmet_each, ncol = 2, nrow = 1, labels = "a", font.label = list(size = 20, color = "black"), widths = c(1, 2))

figure_GSE132203_100_BPmet_each_together <- annotate_figure(figure_GSE132203_100_BPmet_each_together, left = text_grob("BPmet estimate", color = "black", size = 20, rot = 90))
```

@@

GSE132203_100_MethylCIBERSORT_WB <- as.data.frame(cbind(out.l$estF[, 3] + out.l$estF[, 10], out.l$estF[, 5], out.l$estF[, 1], out.l$estF[, 2], out.l$estF[, 4], out.l$estF[, 9]))

@@

melt_GSE132203_100_MethylCIBERSORT_WB <- melt(GSE132203_100_MethylCIBERSORT_WB) %>% cbind(melt_FACS_GSE132203_100$value, .)
colnames(melt_GSE132203_100_MethylCIBERSORT_WB) <- c("FACS", "cell_type", "MethylCIBERSORT")

p_GSE132203_100_MethylCIBERSORT_WB_all <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~"ALL") +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, limits = c(0, 1)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.96), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 5, 1, 2, 4, 9)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)

p_GSE132203_100_MethylCIBERSORT_WB_all_lonly <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~"MethylCIBERSORT") +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, labels = NULL, breaks = NULL) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.96), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 5, 1, 2, 4, 9)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)
#### each cell types

@@

colnames(GSE132203_100_MethylCIBERSORT_WB) <- c("V", "V", "V", "V", "V", "V", "CD4", "CD8", "Mono", "B", "NK", "Neu")

@@

for (i in c(1:6)) {
  rmse[[i]] <- rmse(GSE132203_100_MethylCIBERSORT_WB[, i], GSE132203_100_MethylCIBERSORT_WB[, i + 6])

  melt_GSE132203_100_MethylCIBERSORT_WB[[i]] <- melt(GSE132203_100_MethylCIBERSORT_WB[, c(i, i + 6)], id.vars = colnames(GSE132203_100_MethylCIBERSORT_WB)[i], measure.vars = colnames(GSE132203_100_MethylCIBERSORT_WB)[i + 6])
}

RMSE <- data.frame(
  cell_type = c("CD4", "CD8", "Mono", "B", "NK", "Neu"),
  rmse = unlist(rmse)
)

p_GSE132203_100_MethylCIBERSORT[[1]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[1]], aes(x = value, y = V)) +
  geom_point(colour = c("red"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL) +
  scale_y_continuous(name = NULL) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.245, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.078, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT[[2]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[2]], aes(x = value, y = V)) +
  geom_point(colour = c("green"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.335, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.0772, y = 0.275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)
